\pkg{Rgbp}: An R Package for Gaussian, Poisson, and Binomial Hierarchical Modeling

### 2013-07-31 jss/article.tex
all changes

Next, \code{gbp} will help us fit the Poisson multilevel model with the Gamma conjugate prior distribution on the true death rate $\lambda_{j}$ whose mean is 0.020 ($\lambda_{0}=0.020$) as described in the section 2.2. For reference, the number of regression coefficients ($m$) is 0 because we do not need to estimate the prior mean via log-linear regression (see section 3.2).
\begin{CodeChunk}
\begin{CodeInput}
R> data(hospital)
R> z <- hospital$z
R> n <- hospital$n
R> p <- gbp(z, n, mean.PriorDist = 0.02, model = "pr")
R> p
\end{CodeInput}
\begin{CodeOutput}
Summary for each unit (sorted by n):

@@

In Figure \ref{fig:hospitalcoverage} we see two estimated coverage probabilities: a simple unbiased estimate (a blue dashed line) and an Rao-Blackwellized unbiased estimate (a red line). Both lines are indistinguishable from the horizontal line at 0.95 and the estimated overall average coverage rate is 0.950 from the Rao-Blackwellized estimate. This result shows that the interval estimates from the suggested multilevel modeling on this particular dataset have nice repeated sampling property.

@@

As seen in Figure \ref{fig:schoolcoverage} the desired $95\%$ coverage probability was achieved for each group in this example.

@@

Finally, in Figure \ref{fig:baseball2}, we see that the estimated average coverage probability is 0.973 based on the Rao-Blackwellization, conservatively satisfying the definition of the 95\% confidence interval.

@@

\section[acknowledgments]{Acknowledgments}
The authors would like to thank Phil Everson and the 2012 class of Stat 324r: Parametric Statistical Inference and Modeling for their valuable inputs.
\bibliography{bibliography}

>>>>

Next, \code{gbp} will help us fit the Poisson multilevel model with the Gamma conjugate prior distribution on the true death rate $\lambda_{j}$ whose mean is 0.020 ($\lambda_{0}=0.020$) as described in the section 2.2. For reference, the number of regression coefficients ($m$) is 0 because we do not need to estimate the prior mean via log-linear regression (see section 3.2).
\begin{CodeChunk}
\begin{CodeInput}
R> data(hospital)
R> z <- hospital$d
R> n <- hospital$n
R> p <- gbp(z, n, mean.PriorDist = 0.02, model = "pr")
R> p
\end{CodeInput}
\begin{CodeOutput}
Summary for each unit (sorted by n):

@@

In Figure \ref{fig:hospitalcoverage} we see two estimated coverage probabilities: a simple unbiased estimate (a blue dashed line) and an Rao-Blackwellized unbiased estimate (a red line). Both lines are indistinguishable from the horizontal line at 0.95 and the estimated overall average coverage rate is 0.950 from the Rao-Blackwellized estimate. This result shows that the interval estimates from the suggested multilevel modeling on this particular dataset have nice repeated sampling property. For reference, it took 10 seconds for MacBook Pro with a 2.3 GHz dual-core Intel i5 CPU to run 10,000 simulations.

@@

As seen in Figure \ref{fig:schoolcoverage} the desired $95\%$ confidence (horizontal line at 0.95) is achieved (actually, exceeded) for each school in this example. For reference, it took 188 seconds for 10,000 simulations  on one of authors' MacBook Pro with a 2.3 GHz dual-core Intel i5 CPU. In MCMC, the exact simulation would be too time-consuming. One could compare curve in Figure \ref{fig:schoolcoverage} with a curve from MCMC.

@@

Finally, in Figure \ref{fig:baseball2}, we see that the estimated average coverage probability is 0.973 based on the Rao-Blackwellization, conservatively satisfying the definition of the 95\% confidence interval. As for the running time, it took 243 seconds for MacBook Pro equipped with a 2.3 GHz dual-core Interl i5 CPU to execute 10,000 simulations.

@@

\section[acknowledgments]{Acknowledgments}
The authors would like to thank Phil Everson, Cindy Christiansen, and the 2012 class of Stat 324r: Parametric Statistical Inference and Modeling for their valuable inputs.

\bibliography{bibliography}
